Measurement of deeply virtual Compton scattering off Helium-4

### 2020-01-05 eg6-letters/long-paper/prc-dvcshelium.tex

@@

The reaction measured in the experiment is the coherent electro-production of a photon on helium
$e+^4\!\!He \rightarrow e+\gamma+^4\!\!He$ at high 4-momentum transfer squared ($Q^2$). The leading order diagrams
of this reaction are the coherent DVCS and BH processes. The nuclear coherent DVCS is 
represented in Fig. \ref{fig:CohDiag}. As was detailed in the Chap. \ref{chap:pheno}, 
the two processes interfere at the amplitude level, which give rise to sizable spin asymmetries.
In our experiment, we focused on the measurement of the beam-spin asymmetry (BSA) noted $A_{LU}$ with 
$L$ for the longitudinally-polarized electron beam and $U$ the unpolarized target and defined as:  
\begin{equation}
A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
              {d^{5}\sigma^{+} + d^{5}\sigma^{-}},
  \label{eq:BSA}
\end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the differential cross section for a positive 
(negative) beam helicity. At leading order and leading twist, the BSA can be expressed as:        
\begin{eqnarray}
A_{LU}& =& \frac{x_A(1+\epsilon^2)^2}{y} \, s_1^{INT} \sin(\phi) \, 
\bigg/ \, \bigg[ \, \sum_{n=0}^{n=2}c_n^{BH}\cos{(n\phi)} +  \\
& & \frac{x_A^2 t {(1+\epsilon^2)}^2}{Q^2} P_1(\phi) P_2(\phi) \, c_0^{DVCS} + 
\frac{x_A (1+\epsilon^2)^2}{y} \sum_{n=0}^{n=1} c_n^{INT} \cos{(n\phi)} \bigg].  \nonumber 
\label{eq:coh_BSA}
\end{eqnarray}
where $\mathcal{P}_1(\phi)$ and $\mathcal {P}_2(\phi)$ are the BH 
propagators. The factors: $c_{0,1,2}^{BH}$, $c_0^{DVCS}$, $c_{0,1}^{INT}$ and 
$s_1^{INT}$ are the Fourier coefficients of the BH, the DVCS and the 
interference amplitudes for a spin-zero target \cite{Kirchner:2003wt}. %The explicit 
%expressions of these coefficients can be found in Appendix 
%\ref{app:Helium_cross_section}.

>>>>

The theory of GPDs has been already reviewed in details in various 
publications~\cite{Diehl:2003ny,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya},
we summarized here only necessary elements to discuss our experimental results.
we obtain real structure functions 
$F^{q}(x,\xi,t)$, where $x+\xi$ and $x-\xi$ are the incoming and outgoing quark momenta 
respectively and $t=\Delta^2$ the squared transferred momentum to the target as illustrated in 
Fig. \ref{fig:GPD}.

\begin{figure}[tbp!]
\center
\includegraphics[width=10.0cm]{fig1/GPD.png}
\caption{General representation for the GPDs of a nucleon represented by the triple lines and noted $N$.
	Single lines can represent quarks or anti-quarks probed in the nucleon.}
\label{fig:GPD}
\end{figure}

The different spin states possible lead to several independent GPDs for 
any given hadron. The proper accounting of 
the number of GPDs must be done with regard to the symmetries of the system.
At leading order and leading twist, we find that there are $2(2J+1)^2$ GPDs for a particle of spin $J$, 
$i.e.$ for a spin-0 hadron, like the helium-4 nucleus, we will
have two GPDs, for a spin-1/2 hadron, like the proton, eight GPDs. Half of these involve a 
parton helicity flip, they are called transversity GPDs and do not intervene 
in the DVCS process.

As mentioned above, DVCS is the main experimental access to GPDs. However, this process does not offer
a full access to the GPDs and we only access them integrated over $x$, in the following form:
\begin{equation}
	\int^1 _{-1} dx F^{q}(x,\xi,t) \left [ {1 \over x - \xi - i \epsilon} 
	                                   \mp {1 \over x + \xi - i \epsilon} \right]. 
\end{equation}
To account for this and simplify equations, we define the complex Compton form factors (CFF,
noted with curved $\mathcal{F}$ for a given GPD $F$) for each GPD as follows:
\begin{equation}
	\Re e (\mathcal{F}(\xi,t)) = \sum _q e^2_q \mathcal{P} \int^1_{-1} dx F^{q}(x,\xi,t)
	      \left [ {1 \over x - \xi} \mp {1 \over x + \xi} \right], 
\end{equation}
\begin{equation}
	\Im m (\mathcal{F}(\xi,t)) = - \pi \sum _q e^2_q \left [ F^{q}(\xi,\xi,t) \mp F^{q}(-\xi,\xi,t) \right]. 
\end{equation} 
These are the quantities directly present in the DVCS cross sections. We note that they are summed over
the different quark flavors present in the hadron, as the electromagnetic probe do not differentiate
quark flavors. A similar situation exists for TCS and DVMP giving only a partial access to the GPDs. 
The double DVCS is a special case and it retains the full
dependence of the GPDs in three independent variables.

Experimentally, another process is indistinguishable from the DVCS. This is the Bethe-Heitler (BH) 
process in which % TODO add BH figure
the final state photon is emitted by the scattering lepton rather than the hadron. In this case the 
photon-hadron interaction is the same as in elastic scattering and therefore such process depends on the
target FFs rather than its GPDs. The DVCS and BH processes are experimentally indistinguishable as they
have identical final states, such that they interfere in the squared photo-production amplitude of the
exclusive photo-production process:
\begin{equation}
	|T|^2 = |T_{DVCS}|^2 + |T_{BH}|^2 + T_{DVCS}^* T_{BH} + T_{DVCS}T_{BH}^*. 
\end{equation}
The interference terms increase significantly the cross section in specific parts of the phase space
and lead to significant charge and spin asymmetries.

Finally, we need to define our kinematics properly. We use the 
conventions from Fig. \ref{fig:PhiAngle}. 
In experiments, we generally use slightly different kinematic variables : 
$-t = -(p_p-p_p^\prime)^2 = \Delta^2$ and 
$x = {2\xi \over 1+\xi}$.

\begin{figure}[tbp!]
\center
\includegraphics[width=9cm]{fig1/finalplane.png}
	\caption{Illustration of the scattering (or leptonic) and production (or hadronic) planes
	in the DVCS process.} %TODO upgrade to a figure with phi_S
\label{fig:PhiAngle}
\end{figure}

@@

The reaction measured in the experiment is the coherent electro-production of a photon on helium
$e+^4\!\!He \rightarrow e+\gamma+^4\!\!He$ at high 4-momentum transfer squared ($Q^2$). The 
leading order diagrams
of this reaction are the coherent DVCS and BH processes. The nuclear coherent DVCS is 
represented in Fig. \ref{fig:CohDiag}. As  
the two processes interfere at the amplitude level, which give rise to sizable spin asymmetries.
In our experiment, we focused on the measurement of the beam-spin asymmetry (BSA) noted $A_{LU}$ with 
$L$ for the longitudinally-polarized electron beam and $U$ the unpolarized target and defined as:  
\begin{equation}
A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
              {d^{5}\sigma^{+} + d^{5}\sigma^{-}},
  \label{eq:BSA}
\end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the differential cross section for a positive 
(negative) beam helicity. At leading order and leading twist, the BSA can be expressed as:        
\begin{eqnarray}
A_{LU}& =& \frac{x_A(1+\epsilon^2)^2}{y} \, s_1^{INT} \sin(\phi) \, 
\bigg/ \, \bigg[ \, \sum_{n=0}^{n=2}c_n^{BH}\cos{(n\phi)} +  \\
& & \frac{x_A^2 t {(1+\epsilon^2)}^2}{Q^2} P_1(\phi) P_2(\phi) \, c_0^{DVCS} + 
\frac{x_A (1+\epsilon^2)^2}{y} \sum_{n=0}^{n=1} c_n^{INT} \cos{(n\phi)} \bigg].  \nonumber 
\label{eq:coh_BSA}
\end{eqnarray}
where $\mathcal{P}_1(\phi)$ and $\mathcal {P}_2(\phi)$ are the BH 
propagators. The factors: $c_{0,1,2}^{BH}$, $c_0^{DVCS}$, $c_{0,1}^{INT}$ and 
$s_1^{INT}$ are the Fourier coefficients of the BH, the DVCS and the 
interference amplitudes for a spin-zero target \cite{Kirchner:2003wt}. %The explicit 
%expressions of these coefficients can be found in Appendix 
%\ref{app:Helium_cross_section}.
